Malacology: A Programmable Storage System Built on Ceph

### 2016-05-09 paper/paper.tex
logical storage devices
Signed-off-by: Noah Watkins <noahwatkins@gmail.com>

\subsection{Durability}\label{durability}

@@

\subsection{Active Storage}\label{active-storage}

Active storage attempts to push computation closer to the data by
exposing interfaces to execute code remotely. For example, the storage
server could process data before sending data over the network or
sorting it. The active storage component in Ceph is called ``object
interface classes'' (or \texttt{cls} for short). The Ceph object
interface classes can be loaded at runtime and customized with
user-defined functionality. The basic idea is shown in
Figure\textasciitilde{}\ref{fig:object-interfaces}, where the
\texttt{libcls\_md5.so} shared library performs the MD5 hash on an
object at the oSD instead of transferring data over the network. This
ability to carry out arbitrary operations on objects stored on OSDs
helps applications improve performance by optimizing things like network
round trips, data movement, and remote resources which may be idle.

Object storage interfaces are compiled into shared libraries and loaded
into a running OSD daemon using \texttt{dlopen()}. Because the shared
library has to link against symbols found in the running executable, the
interfaces are stored on the local file systems of each OSD so they can
be versioned and distributed alongside the same Ceph binaries. This
policy is for safety, since the OSDs could be on different distros that
provide different versioning capabilities. Also, this approach allows
bug fixes to co-evolve with the rest of the Ceph installation.

Although customizable OSD interfaces are powerful, the current
implementation has drawbacks. OSD interfaces are written in C/C++ and
compiled into a shared library, so the developer must account for
different target architectures. Second, C/C++ provides more
functionality than is necessary since the snippets of interface code
mainly set policies and perform simple operations. Finally, developing
these interfaces in C/C++ has high overhead. The developer must learn
how the OSD dynamically loads the shared libraries (\emph{e.g.}, OSDs
rely on a strict naming convention to find shared libraries), how to get
their interfaces compiled using the Ceph \texttt{make} system, and how
to debug issues that are not related to their specific interface
(\emph{e.g.}, the OSD cannot find the shared library) - this learning
curve is unacceptable for non-Ceph developers, especially since most
interfaces are one-off solutions specific to their applications.

Ceph has a whole infrastructure for getting dynamic code into the OSD.
The \texttt{ClassHandler} class safely opens object interfaces, executes
commands defined by the shared library, and fails gracefully with
helpful errors if anything goes wrong. Instead of injecting strings
directly into Ceph (like we did with the original Mantle
implementation), the \texttt{ClassHandler} class safely opens shared
code, even code with dependencies that are not in Ceph itself (e.g.,
Lua). With the \texttt{ClassHandler}, we get the safety and robustness
of loading dynamic code, the ease of transferring state between object
interfaces and the oSD internals, integration with testing and
correctness suites, and \texttt{struct}s for interface data and
handlers.

While we consider active storage to be an excellent example of
programmability, what separates our proposal from previous work is the
observation that so much \emph{more} of the storage system can be reused
to construct advanced, domain-specific interfaces.

@@

>>>>

\subsection{Durability}
\label{sec:durability}

@@

\subsection{Logical Storage Devices}
\label{active-storage}

Ceph provides a rich plugin framework for defining new interfaces to objects
stored within RADOS, effectively allowing developers to use co-design
techniques to define logical storage devices tailored to their application
domain.

An object interface plugin is structured in a similar way to that of an RPC in
which a developer creates a named function within the cluster that clients may
invoke upon an object. In Ceph these functions are defined by a composition of
existing native interfaces that include reading and writing bytestream data
and controlling snapshots and cloning, all of which may be transactionally
composed with full access to a sorted key-value service allowing applications
to fine tune storage interfaces, such as using a read-modify-write guard to
protect shared data.

Although this feature is powerful, the current implementation has drawbacks.
Supporting only C/C++ for object interface developers, Ceph requires
distribution of compiled binaries for the correct architecture, adding a
large barrier of entry for developers and system administrators. Second,
having no way to dynamically unload modules, any changes require a full
restart of an OSD which may have serious performance impacts due to a loss
of cached data. And finally, the security limitations of the framework
limit the use of object classes to all but those with administrative level
access and technique expertise.

@@

\section{Related Work}
